{\normalsize \textbf{Vagueness and imprecise imitation in signalling games}}

### 2016-06-10 paper/version_final/paper_clean_format.tex
final version

\documentclass[12pt,english]{article}
\usepackage{etex}

@@

\usepackage[]{../../helpers/mypackages}
%\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
\usepackage{../../helpers/myenvironments}
\usepackage{../../helpers/mycommands}
%\usepackage{todonotes}
\usepackage{subcaption}

@@

\usepackage[nomarkers, nolists]{endfloat}

@@

% spacing
\usepackage{setspace}
\doublespacing

% left justification:
\raggedright

% indentation
\setlength\parindent{12pt}

% section headings
\usepackage{sectsty}
\allsectionsfont{\normalsize\raggedright\centering}

% table of contents stuff
\setcounter{tocdepth}{2}
\usepackage[]{tocloft}
\addtocontents{toc}{\cftpagenumbersoff{section}}
\addtocontents{toc}{\cftpagenumbersoff{subsection}}
\renewcommand{\cftsecfont}{\itshape}
\renewcommand{\cftsubsecfont}{\itshape}
\makeatletter
\renewcommand{\@cftmaketoctitle}{}
\makeatother
\renewcommand{\cftdot}{}

% footnotes
\usepackage[]{footmisc}
\renewcommand\footnotelayout{\normalsize\doublespacing\raggedright}

@@

% FONTS:
%-------
% for times roman fonts:
\usepackage{txfonts}
% recommended if output will have accented characters:
\usepackage[T1]{fontenc}
% recommended if inputting accented directly from the keyboard:
%\usepackage[latin1]{inputenc}

% BJPS specific cite commands:
\newcommand{\citetbjps}[1]{\citeauthor{#1} ([\citeyear{#1}])}
\newcommand{\citetbjpspost}[2]{\citeauthor{#2} ([\citeyear{#2}], #1)}
\newcommand{\citealtbjps}[1]{\citeauthor{#1} [\citeyear{#1}]}
\newcommand{\citepbjps}[1]{(\citeauthor{#1} [\citeyear{#1}])}
\newcommand{\citepbjpspre}[2]{(#1~\citeauthor{#2} [\citeyear{#2}])}
\newcommand{\citeyearbjps}[1]{[\citeyear{#1}]}
\newcommand{\citeyearparbjps}[1]{([\citeyear{#1}])}

@@

\title{{\normalsize \textbf{Vagueness and imprecise imitation in signalling games}}}
\author{{\normalsize \textbf{Michael Franke}} \and {\normalsize \textbf{Jos\'e Pedro Correia}}}
\date{}

@@

\mbox{} \\

\tableofcontents

\mbox{} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{flushright}
Michael Franke \\
Wilhelmstra\ss e 19 \\
Department of Linguistics \\
University of T\"ubingen \\
72072 T\"u bingen \\
Germany \\
\texttt{mchfranke@gmail.com} \\
\bigskip
Jos\'e Pedro Correia \\
Via Panorâmica s/n \\
Institute of Philosophy \\
Faculty of Arts \\
University of Porto \\
4150-564 Porto \\
Portugal \\
\texttt{zepedro.correia@gmail.com} \\
\end{flushright}

\bibliographystyle{bjps}
\bibliography{../../helpers/MyRefGlobal,paper}

>>>>

\documentclass[11pt,english]{article}
\usepackage{etex}

@@

\usepackage[]{mypackages}
%\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
\usepackage{myenvironments}
\usepackage{mycommands}
%\usepackage{todonotes}
\usepackage{subcaption}

@@

% \usepackage[nomarkers, nolists]{endfloat}

@@

% spacing
% \usepackage{setspace}
% \doublespacing

% left justification:

% % indentation
% \setlength\parindent{12pt}

% % section headings
% \usepackage{sectsty}
% \allsectionsfont{\normalsize\raggedright\centering}

% % table of contents stuff
% \setcounter{tocdepth}{2}
% \usepackage[]{tocloft}
% \addtocontents{toc}{\cftpagenumbersoff{section}}
% \addtocontents{toc}{\cftpagenumbersoff{subsection}}
% \renewcommand{\cftsecfont}{\itshape}
% \renewcommand{\cftsubsecfont}{\itshape}
% \makeatletter
% \renewcommand{\@cftmaketoctitle}{}
% \makeatother
% \renewcommand{\cftdot}{}

% % footnotes
% \usepackage[]{footmisc}
% \renewcommand\footnotelayout{\normalsize\doublespacing\raggedright}

@@

% FONTS:
%-------
% for times roman fonts:
% \usepackage{txfonts}
% recommended if output will have accented characters:
% \usepackage[T1]{fontenc}
% recommended if inputting accented directly from the keyboard:
%\usepackage[latin1]{inputenc}

% BJPS specific cite commands:
\newcommand{\citetbjps}[1]{\citeauthor{#1} (\citeyear{#1})}
\newcommand{\citetbjpspost}[2]{\citeauthor{#2} (\citeyear{#2}, #1)}
\newcommand{\citealtbjps}[1]{\citeauthor{#1} \citeyear{#1}}
\newcommand{\citepbjps}[1]{(\citeauthor{#1} \citeyear{#1})}
\newcommand{\citepbjpspre}[2]{(#1~\citeauthor{#2} \citeyear{#2})}
\newcommand{\citeyearbjps}[1]{\citeyear{#1}}
\newcommand{\citeyearparbjps}[1]{(\citeyear{#1})}

@@

\title{{\normalsize \textbf{Vagueness and imprecise imitation in signalling games}}}
\author{{\normalsize {Michael Franke \& Jos\'e Pedro Correia}}}
\date{}

@@

@@

\bibliographystyle{apalike}
\bibliography{bibexport}
